Universal Anonymous Signatures

### 2022-06-08 prism-backend/research/gsac/security-uas.tex
Updated UAS proofs. Missing proof for new property obt-anon.

\begin{theorem}[Non-frameability of \CUASGen]
  \label{thm:frame-uas}
  If the underlying scheme for $\NIZK^{\Issue}$ is zero-knowledge, the scheme
  for $\NIZK^{\Sign}$ is zero-knowledge, sound and simulation-extractable, the
  scheme for $\NIZK^{\Open}$ is zero-knowledge and sound, and the commitment
  scheme is hiding, then our \CUASGen construction satisfies non-frameability as
  defined in \defref{def:frame-uas}, except with negligible probability.
\end{theorem}

\begin{proof}[\thmref{thm:frame-uas}; Non-frameability of \CUASGen]
  First, note that the adversary wins if it produces a signature that traces to
  an honest user (which, in our case, is tested by checking whether the
  extracted \usk belongs ot an honest user); and, in addition, either (1) the
  signature was not produced via a call to the \SIGN oracle, or (2) the opening
  value output by the adversary and accepted by \Judge, does not match the
  extracted one (i.e., the one used as witness to $\NIZKRel^{\Sign}$). Note that
  the probability of (2) is negligible due to soundness of $\NIZK^{\Sign}$ and
  $\NIZK^{\Open}$, given that \Verify and \Judge accept the signature and
  opening proof.

  Next we prove that, given an adversary $\adv$ against non-frameability of
  \CUASGen, under condition (1) above, we can build an adversary \advB that
  breaks the hiding property of the underlying commitment scheme, with
  non-negligible probability.

  We start from $G_0=\ExpNonframe$. $\adv$ makes queries to the oracles in
  \Oframe.

  For $G_1$, within \Setup, we replace the \Setup algorithms for the three
  NIZKs (\Issue, \Sign and \Open) with their corresponding \SimSetup
  variants. Consequently, the corresponding queries to \Prove are also
  simulated via the simulator. By the zero-knowledge property of the NIZK
  systems, $G_1$ is indistinguishable from $G_0$.

  We build adversary \advB against hiding of commitments from $G_1$ against
  non-frameability. In the hiding game (see \figref{fig:com-games}), \advB first
  picks two messages $\msg_0$ and $\msg_1$, and then receives a commitment \Ccom
  of $\msg_b$. Let \advB pick both $\msg_0$ and $\msg_1$ from \AttrSpace. Then,
  \advB initializes $G_1$ for $\adv$ against non-frameability, and randomly
  picks a number $u \getr [1,q]$, where $q$ can be as large as \advB wants, but
  will be the maximum number of honest users to let $\adv$ add to the game.
  Then, when $\adv$ asks to create the $u$-th user, \advB ignores the call to
  \UKeyGen. For every call that $\adv$ makes to the \OBTAIN oracle associated to
  the $u$-th user, \advB uses the commitment \Ccom received as challenge in its
  game against the hiding property of commmitments, and uses it as commitment to
  the $u$-th user's \usk. \advB then simulates all the NIZK proofs associated to
  the $u$-th user, in calls to \OBTAIN, \SIGN and \INSPECT. Again, due to the
  zero-knowledge property of the associated NIZK systems, the outputs of the
  modified oracles are indistinguishable from the original outputs (as \Ccom
  is a valid commitment of a user secret key). Eventually, $\adv$ outputs a
  $(\sig,\yeval,\msg,\feval,\yinsp,\iproof)$ tuple that is accepted by \Verify
  and \Judge. Due to simulation extractability of $NIZK^{\Sign}$, \ExtractSign
  must be able to produce a $(\usk,\scred,\attrs_{\scred},\yinsp')$ tuple. Since
  $\adv$ wins the non-frameability game, with probability $1/q$,
  the \usk value belongs to the $u$-th honest user, so it must be equal to
  either $\msg_0$ or $\msg_1$; \advB responds accordingly to its challenge in
  the game for the hiding property of the commmitment scheme. By assumption,
  \advB wins with non-negligible probability.
  %
  \qed
\end{proof}

>>>>

\begin{theorem}[Non-frameability of \CUASGen]
  \label{thm:frame-uas}
  If the underlying scheme for $\NIZK^{\Issue}$ is zero-knowledge, the schemes
  for $\NIZK^{\Sign}$ are zero-knowledge and simulation-extractable, and the
  commitment scheme is hiding, then our \CUASGen construction satisfies
  non-frameability as defined in \defref{def:frame-uas}, except with negligible
  probability.
\end{theorem}

\begin{proof}[\thmref{thm:frame-uas}; Non-frameability of \CUASGen]
  We prove that, given an adversary $\adv$ against non-frameability of
  \CUASGen, we can build an adversary \advB that breaks the hiding property of
  the underlying commitment scheme, with non-negligible probability.

  We start from $G_0=\ExpNonframe$. $\adv$ makes queries to the oracles in
  \Oframe. For $G_1$, within \Setup, we replace the \Setup algorithms for the
  three NIZKs (\Issue, \Sign and \Open) with their corresponding \SimSetup
  variants. Consequently, the corresponding queries to \Prove are also
  simulated via the simulator. By the zero-knowledge property of the NIZK
  systems, $G_1$ is indistinguishable from $G_0$. In the sequel, we build on
  top of $G_1$, depending on whether or not a matching \Sig is found in \SIG,
  in line 7.

  \paragraph{(a) A matching \Sig exists in \SIG.} %
  If we can find a matching \Sig in \SIG, for some \uid, then \adv~does not win
  at line 7 of the game. Given that the signature is accepted by \Verify at line
  3, and after simulation extractability of $\NIZK^{\Sign}$, $\yeval =
  \yeval^0$, and $\tyeval^1 = \yeval^1$. Similarly, since the $(\yinsp,\iproof)$
  pair output by \adv~is accepted by \Judge, simulation extractability of
  $\NIZK^{\Sign}$ and $\NIZK^{\Open}$ implies that both checks at line 9 pass.
  Hence, the probability that the adversary wins at either lines 8 or 9 is $0$,
  after simulation extractability of $\NIZK^{\Sign}$ and $\NIZK^{\Open}$.

  \paragraph{(b) No matching \Sig exists in \SIG.} %
  This means that \adv~creates an \UAS forgery. We leverage such an adversary
  against $G_1$ to break the hiding property of the underlying commitment
  scheme (see \appref{sapp:commitments}). For each new honest user \uid creation
  request by \adv~(via \HUGEN),
  \advB leverages its own $COM$ oracle to embed its challenges in the commitment
  scheme into credentials of the \UAS non-frameability game. More precisely, in
  calls to \HUGEN by \adv, \advB does not call \UKeyGen and instead picks two
  random messages, $\msg_0^{\uid},\msg_1^{\uid}$, both from \AttrSpace. Whenever
  a query to \OBTAIN is made by \adv~on behalf of \uid, \advB makes a call to
  its $COM$ oracle, to get a commitment \Ccom for $\usk^{\uid}=\msg_b^{\uid}$
  (for \advB's challenge bit $b$). Then,  \advB uses \Ccom in its \SBCMCom part
  of the underlying \SBCM interactive signing protocol, and simulates the
  corresponding $\NIZK^{\Issue}$ proof. Due to the zero-knowledge property, the
  produced output is indistinguishable to that of the real execution. Similarly,
  \advB can simulate the calls to the \SIGN and \OPEN oracles due to
  simulation extractability of $\NIZK^{\Sign}$ and $\NIZK^{\Open}$.
  %
  Eventually, $\adv$ outputs a $(\oid,\siid,\Sig,\msg,\feval,\yinsp,\iproof)$
  tuple that is accepted by \Verify and \Judge. Due to simulation extractability
  of $NIZK^{\Sign}$, \ExtractSign must be able to produce a $(\usk,\scred,
  \attrs_{\scred}, \tyeval^1,\yinsp')$ tuple. As, by assumption (line 6),  there
  exists an \uid matching that \usk, all \advB has to do is find the
  \uid for which \usk was used as either $\msg_0$ or $\msg_1$ in its hiding
  game. Thus, \advB wins its hiding game with the same probability than \adv~
  has to win the non-frameability game.
  %
  \qed
\end{proof}
